\chapter*{Acknowledgements}

First, I would like to thank my thesis advisor, Dr. Dimitri Komatitsch, who provided me a large amount of skills and knowledge on high-performance computing and wave propagation,
also with is very skilled team, and introduced me to the greatly-composed numerical code SPECFEM, while still dynamically and rapidly advancing its development at the same time.

I would also like to thank Prof. Joseph Moysan, who is the co-advisor of this thesis and decided to hire me and bring me over from a country very far, and, during the whole period of this Ph.D., especially gave me support to not only my study by his rich knowledge on acoustics but also about living in France.

I am also grateful to Dr. Christian Lhuillier, who supported me at CEA Cadarache and gave me his abundant knowledge and experience on acoustics and engineering in nuclear reactors.

I also thank the other members of the laboratories, including CEA Cadarache DTN/STCP/LISM and CNRS LMA Marseille, who kindly helped and warmly welcomed me.

I would also thank all the members of the jury of this Ph.D., Prof. Mounsif Ech-Cherif El-Kettani, Dr. Michel Darmon, Dr. St\'ephane Lanteri, Dr. Antoine Gerschenfeld and Dr. Dominique Habault for their kind acceptance to be in the jury, for their careful verification on my Ph.D. report, and for attending my defense.

I thank Dr. Antoine Gerschenfeld and Dr. Pierre-Emmanuel Angeli (CEA/DANS/DM2S/STMF) who provided us the CFD calculation data and instructions on the visualization and interpolation tools that were essentials for obtaining our results and progressing in our research.

I would also like to express my gratitude to Mr. Greg Sjaardema from Sandia National Laboratories, USA, for kindly supporting us on how to use the EXODUS-II mesh format and its management toolkit SEACAS.

Parts of this work were granted access to the French HPC resources of TGCC/CINES under allocations 2016107626, 2016047165 and 2016047748 made by GENCI. We are deeply grateful to GENCI for that.
